PANCHANGE_data_preprocessing

### 2020-08-07 PANCHANGE_data_preprocessing2020-07-15.Rmd
added half a year sign up difference coping and prepandemic

```{r coping glad gad cleaning}
coping.glad.gad.raw.id <- coping.glad.gad.raw %>%
  drop_na(externalDataReference) %>% # Drop NAs
  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  mutate(ID = as.numeric(ID),
         startDate.glad = startDate) %>% # Rename startDate
  select(
    Sample, # Sample
    ID, # ID
    startDate.coping.glad = startDate,
    gad.problems_made_difficult_care, # Impairment
    gad.pandemic_felt_feelings, # Comparison to before the pandemic (retro)
    gad.feeling_nervous_anxious_or_on_edge_retro = gad.feeling_nervous_anxious_or_on_edge,
    gad.control_worrying_stop_retro = gad.control_worrying_stop,
    gad.worrying_too_much_about_different_things_retro = gad.worrying_too_much_about_different_things,
    gad.trouble_relaxing_retro = gad.trouble_relaxing,
    gad.sit_restless_hard_retro = gad.sit_restless_hard,
    gad.becoming_easily_annoyed_or_irritable_retro = gad.becoming_easily_annoyed_or_irritable,
    gad.awful_feeling_afraid_happen_retro = gad.awful_feeling_afraid_happen,
    gad.feeling_nervous_anxious_or_on_edge_base = gad.feeling_nervous_anxious_or_on_edge.1,
    gad.control_worrying_stop_base = gad.control_worrying_stop.1,
    gad.worrying_too_much_about_different_things_base = gad.worrying_too_much_about_different_things.1,
    gad.trouble_relaxing_base = gad.trouble_relaxing.1,
    gad.sit_restless_hard_base = gad.sit_restless_hard.1,
    gad.becoming_easily_annoyed_or_irritable_base = gad.becoming_easily_annoyed_or_irritable.1,
    gad.awful_feeling_afraid_happen_base = gad.awful_feeling_afraid_happen.1
  ) %>%
  add_numeric(., exclude = exclude_cols) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

@@

```{r coping glad ocir cols}
coping.glad.ocir.raw <- readRDS(file = paste0(data.raw_path, "/2020-08-04/glad/ocir_coping_glad.rds"))
dim(coping.glad.ocir.raw)
colnames(coping.glad.ocir.raw)
```

@@

table(dat.glad$over_one_year_time_diff_sign_up_coping)
```

>>>>

```{r coping glad gad cleaning}
exclude_cols_coping_glad <- c(
  "Sample",
  "ID",
  "startDate.coping.glad"
)

coping.glad.gad.raw.id <- coping.glad.gad.raw %>%
  drop_na(externalDataReference) %>% # Drop NAs
  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  mutate(ID = as.numeric(ID),
         startDate.glad = startDate) %>% # Rename startDate
  select(
    Sample, # Sample
    ID, # ID
    startDate.coping.glad = startDate,
    gad.problems_made_difficult_care, # Impairment
    gad.pandemic_felt_feelings, # Comparison to before the pandemic (retro)
    gad.feeling_nervous_anxious_or_on_edge_retro = gad.feeling_nervous_anxious_or_on_edge,
    gad.control_worrying_stop_retro = gad.control_worrying_stop,
    gad.worrying_too_much_about_different_things_retro = gad.worrying_too_much_about_different_things,
    gad.trouble_relaxing_retro = gad.trouble_relaxing,
    gad.sit_restless_hard_retro = gad.sit_restless_hard,
    gad.becoming_easily_annoyed_or_irritable_retro = gad.becoming_easily_annoyed_or_irritable,
    gad.awful_feeling_afraid_happen_retro = gad.awful_feeling_afraid_happen,
    gad.feeling_nervous_anxious_or_on_edge_base = gad.feeling_nervous_anxious_or_on_edge.1,
    gad.control_worrying_stop_base = gad.control_worrying_stop.1,
    gad.worrying_too_much_about_different_things_base = gad.worrying_too_much_about_different_things.1,
    gad.trouble_relaxing_base = gad.trouble_relaxing.1,
    gad.sit_restless_hard_base = gad.sit_restless_hard.1,
    gad.becoming_easily_annoyed_or_irritable_base = gad.becoming_easily_annoyed_or_irritable.1,
    gad.awful_feeling_afraid_happen_base = gad.awful_feeling_afraid_happen.1
  ) %>%
  add_numeric(., exclude = exclude_cols_coping_glad) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

@@

```{r coping glad ocir cols}
coping.glad.ocir.raw <- readRDS(file = paste0(data.raw_path, "/glad/ocir_coping_glad.rds"))
dim(coping.glad.ocir.raw)
colnames(coping.glad.ocir.raw)
```

@@

dat.glad %>%
  freq(over_one_year_time_diff_sign_up_coping, cumul = F)
```

Proportion of people signed up over one year ago
```{r eval=FALSE, include=FALSE}
dat.glad <- dat.glad %>%
  mutate(
    over_half_a_year_time_diff_sign_up_coping_numeric =
      as.numeric(
        if_else(time_diff_sign_up_coping > 182.5, 1, 0
                )
      )
  )

dat.glad <- dat.glad %>%
  mutate(
    over_half_a_year_time_diff_sign_up_coping =
      recode_factor(
        over_half_a_year_time_diff_sign_up_coping_numeric,
        "0" = "Sign up under half a year before COPING",
        "1" = "Sign up over half a year before COPING"
      )
  )

dat.glad %>%
  freq(over_half_a_year_time_diff_sign_up_coping, cumul = F)
```
